Proposal full title \\ Proposal Acronym

### 2001-10-04 drafts/IST/PartA.tex
objectives
svn path=/trunk/; revision=1475

\documentclass[a4paper,11pt]{report}
\usepackage[latin1]{inputenc}
\begin{document}
\section*{Notice}
This file will be generated by Protool. Thus layout does not matter. It will
juste be cut\&paste.
\section*{A1 Administrative Overview}
\subsection*{Summary}
\begin{tabular}{|c|c|}
\hline
Proposal Acronym &  \\ \hline
Proposal Number &  \\ \hline
Thematic Priorities & IST-2001-4.3.3. \\ \hline
Call identifier & \\ \hline
Proposal Date & 16 10 2001 \\ \hline
Proposal full name & \\ \hline
\end{tabular}
\subsection*{Abstract (1000 characters)}
\textit{The proposal abstract should be a very short and precise presentation
of the main features of the proposal. Why is it proposed and what problem is it
solving? What are the objectives? How will the objectives be achieved? What
results are expected? This proposal abstract will be used together with the
proposal summary description in form A2 in the evaluation process and in
communications about the proposals to the interested parties (Commission
services and programme committees, etc.). Please use plain typed text, avoiding
formulae and other special characters. If the proposal is written in a language
other than English, please include in form A1 an English version of the
abstract.} \\ \\ \\
In almost two years, the biggest barriers for Free Software development have
been raised by the hosting facilities which provide most of the mandatory tools
that free software developers need for everyday tasks. But although there are
many hosting facilities around the world, no software package is designed to
setup and maintain a set of machines dedicated to this purpose. The NAME
project will provide a generic solution that can be used and adapted by all of
them. Furthermore it will focus on the ease of installation which will fix the
biggest drawback of the current solutions.
\\ \\ 
586 characters
\begin{tabular}{|c|c|}
\hline
Duration in months & \\ \hline
Keyword & BESTP \\ \hline
\end{tabular}
\section*{A2 Proposal Summary}
\textit{This form, should be filled in by the co-ordinator only, for single
participant proposals by the principal contractor. You should not use more than
3,500 characters. The proposal summary should, at a glance, provide the reader
with a clear understanding of the proposal objectives and how the objectives
will be achieved, and their relevance in the context of the objectives of the
specific programme. This summary may be used as an alternative to the proposal
abstract, as the description of the proposal in the evaluation process and in
communications to the programme management committees and other interested
parties. It must therefore be short and precise. Please use plain typed text,
avoiding formulae and other special characters. If the proposal is written in a
language other than English, please include in form A2 an English version of
the proposal summary.} \\

\subsection*{Objectives (max 1000 characters)}
to be written
\subsection*{Description of the work (max 2000 characters)}
to be written
\subsection*{Milestones and expected result (max 500 characters)}

>>>>

\documentclass[a4paper,11pt]{report}
\usepackage[latin1]{inputenc}
\begin{document}
\section*{Notice}
This file will be generated by Protool. Thus layout does not matter. It will
juste be cut\&paste.
\section*{A1 Administrative Overview}
\subsection*{Summary}
\begin{tabular}{|c|c|}
\hline
Proposal Acronym &  \\ \hline
Proposal Number &  \\ \hline
Thematic Priorities & IST-2001-4.3.3. \\ \hline
Call identifier & \\ \hline
Proposal Date & 16 10 2001 \\ \hline
Proposal full name & \\ \hline
\end{tabular}
\subsection*{Abstract (1000 characters)}
\textit{The proposal abstract should be a very short and precise presentation
of the main features of the proposal. Why is it proposed and what problem is it
solving? What are the objectives? How will the objectives be achieved? What
results are expected? This proposal abstract will be used together with the
proposal summary description in form A2 in the evaluation process and in
communications about the proposals to the interested parties (Commission
services and programme committees, etc.). Please use plain typed text, avoiding
formulae and other special characters. If the proposal is written in a language
other than English, please include in form A1 an English version of the
abstract.} \\ \\ \\
In almost two years, the biggest barriers for Free Software development have
been raised by the hosting facilities which provide most of the mandatory tools
that free software developers need for everyday tasks. But although there are
many hosting facilities around the world, no software package is designed to
setup and maintain a set of machines dedicated to this purpose. The NAME
project will provide a generic solution that can be used and adapted by all of
them. NAME will of course provide the same services as current facilities but
will focus an the ease of configuration and installation that all current ones
lack.
\\ \\ 
628 characters...
\begin{tabular}{|c|c|}
\hline
Duration in months & \\ \hline
Keyword & BESTP \\ \hline
\end{tabular}
\section*{A2 Proposal Summary}
\textit{This form, should be filled in by the co-ordinator only, for single
participant proposals by the principal contractor. You should not use more than
3,500 characters. The proposal summary should, at a glance, provide the reader
with a clear understanding of the proposal objectives and how the objectives
will be achieved, and their relevance in the context of the objectives of the
specific programme. This summary may be used as an alternative to the proposal
abstract, as the description of the proposal in the evaluation process and in
communications to the programme management committees and other interested
parties. It must therefore be short and precise. Please use plain typed text,
avoiding formulae and other special characters. If the proposal is written in a
language other than English, please include in form A2 an English version of
the proposal summary.} \\
\subsection*{Objectives (max 1000 characters)}
The NAME project aims at developping a complete hosting facility. It composed
of two subprojects. \\
The first one is the NAME project that will be a next generation hosting
facility. It will provide a web frontend to a number of tools are now mandatory
for software development (user/groups rights management, bug tracking, mailing
lists and forums...). The main idea between its design is to make it
transparently distributed. At each step of its development, we will focus on
the ease of installation and configuration.
The second one is the "CoopX" project that will provide a generic description of
an hosting facility. With that tool we want to allow different kind of facility
to communicate each other. It will help to develop tools to facilitate
migrations between hosting facilities.
\\ 800 chars need some check and some other stuff:w
\subsection*{Description of the work (max 2000 characters)} to be written
\subsection*{Milestones and expected result (max 500 characters)}

### 2001-10-04 drafts/IST/PartB.tex
objectives
svn path=/trunk/; revision=1475

more info : http://www.cordis.lu/ist/bwp_en5.htm
\end{verbatim}
\maketitle
\tableofcontents
\chapter*{B3. Objectives}
\textit{This section, which should not exceed two pages, describes the
scientific/technological objectives of the proposal. They should be achievable
within the project, not through subsequent development, and should be stated in
a measurable and verifiable form. The Progress of the Take-Up action will be
measured against theses objectives in later reviews and assessments.\\
This section should clearly specify in addition to the technical objectives -
also the quantified business objectives and how they are measured}
\\ \\
to be written
\chapter*{B4. Contribution to program/Key action objectives}
\textit{This section, which should not exceed more than one page, describes how
the proposed Take-Up Action will contribute to the objectives of the program
and Key action. This can be done by describing how the proposal meets the
objectives and focus of the Action line which it addresses}
\\ \\
to be written
\chapter*{B5. Innovation}
\textit{This section, not exceeding two pages, describes the innovative
aspects of the proposed project. \\
Progress beyond the state of current practices within a user organization
should be described. The individual action steps must be described in the
context of the real business case. A separate description of this underlying
baseline project/target application - in terms of technical and business
parameters - must be included. Choice and justification for each of the new
practices including the supporting technologies (with comparison of not chosen
options) should be given (e.g. new methodologies, technologies, hardware and/or
software tools, subcontracted experts etc. -- whatever is applicable for the
experiment.}
\\ \\
to be written.
\chapter*{B6. Project workplan}
\textit{This section concisely describes the work planned to achieve the
objectives of the proposed Take-Up Action. The recommended length, excluding
the forms specified below, is up to 10 pages. An introduction should explain
the structure of the workplan and how the workplan must be broken into
workpackages (WPs) which should follow the logical phases of the projects'
life, and include management of the project and assessment of progress and
results. \\ \\
There must be a separate WP each for 'measurement and evaluation of results}
\\ \\ not yet written
\end{document}

>>>>

more info : http://www.cordis.lu/ist/bwp_en5.htm
\end{verbatim}
\maketitle
\tableofcontents
\chapter*{some text}
%%%%%%%%%%%%%%%%%%%
\subsubsection{Context}
Most of free or open source software is collaboratively developped using an
hosting plateform. They are mostly web sites. The frontend integrates different
functionnalities that are available to project developpers and administrators
and linked them with each other. The backend is mainly implemented with
scripts. \\
Current hosting plaforms are implemented as a  web site that provides
functionnalities to developpers. The most common ones include  users and groups
of users management, project repository (usualy based on Concurent Versionning
System), per project web pages and document sharing, per project mailing lists
and web forums, bugtracking system, project management system (audit, task
management), global site management and information feeding. There is currently
four main web hosting facilities : SourceForge (http://sourceforge.net/),
Savannah (http://savannah.gnu.org/), VHFFS (http://tuxfamily.org/), nd
Picolibre (http://picolibre.eu.org/). In terms of number of users and projects,
Savannah and SourceForge are the leaders.
\subsubsection{Mission}
Although hosting facilities are widely used in the freesoftware community the
existing solutions have some drawbacks, that refrain their wide adoption as
well in the Libre software community than in the software industry. \\
Due to a quick design, they are hard to distribute. They mainly are a front end
to a group of dedicated machines that provides a precise set of
functionnalities. Even if the acces is remote, all data is centralized as one
site physically hosts an huge number of projects. This is bad practice in terms
of data safety, data access and scalability. \\
Also due to the number of services and their inter-relations, it is not simple
to set up a new site that provides hosting. This is a real brake to a large
number of sites using this technology.  There is no complete solutions to
install easily any of the technologies described above. \\
They rely too much on managing procedures and human control. For example, a
site needs to be managed by people that acknowledge project creation. \\
At last the most active effort to build such a sytem has recently become
proprietary.  Therefore the produced work is not available. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{B3. Objectives}
\textit{This section, which should not exceed two pages, describes the
scientific/technological objectives of the proposal. They should be achievable
within the project, not through subsequent development, and should be stated in
a measurable and verifiable form. The Progress of the Take-Up action will be
measured against theses objectives in later reviews and assessments.\\
This section should clearly specify in addition to the technical objectives -
also the quantified business objectives and how they are measured}
\\ \\
to be written
\chapter*{B4. Contribution to program/Key action objectives}
\textit{This section, which should not exceed more than one page, describes how
the proposed Take-Up Action will contribute to the objectives of the program
and Key action. This can be done by describing how the proposal meets the
objectives and focus of the Action line which it addresses}
\\ \\
to be written
\chapter*{B5. Innovation}
\textit{This section, not exceeding two pages, describes the innovative
aspects of the proposed project. \\
Progress beyond the state of current practices within a user organization
should be described. The individual action steps must be described in the
context of the real business case. A separate description of this underlying
baseline project/target application - in terms of technical and business
parameters - must be included. Choice and justification for each of the new
practices including the supporting technologies (with comparison of not chosen
options) should be given (e.g. new methodologies, technologies, hardware and/or
software tools, subcontracted experts etc. -- whatever is applicable for the
experiment.}
\\ \\
to be written.
\chapter*{B6. Project workplan}
\textit{This section concisely describes the work planned to achieve the
objectives of the proposed Take-Up Action. The recommended length, excluding
the forms specified below, is up to 10 pages. An introduction should explain
the structure of the workplan and how the workplan must be broken into
workpackages (WPs) which should follow the logical phases of the projects'
life, and include management of the project and assessment of progress and
results. \\ \\
There must be a separate WP each for 'measurement and evaluation of results}
\\ \\ not yet written
\end{document}
